Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-02-17 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
added short intro to section IV

%%%%%%%%%%%%%%%%%
\section{Results using LIGO-Virgo events}
\label{sec:results}
%%%%%%%%%%%%%%%%%
\subsection{Parameter Inference}

@@

%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
%
%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).
Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method. In~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis in Sec.VIII A.2 (which is most similar to the \pSEOB{} model presented in this paper) identified two events which provided the strongest bounds on the dominant QNM measuments -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.

\ag{event selection, noise, PE settings, priors}

>>>>

%%%%%%%%%%%%%%%%%
\section{Results using LIGO-Virgo events}
\label{sec:results}

In this section, we provide a basic outline of the Bayesian formalism we use to infer the properties of the underlying GW signal, identify the most promising events from the catalog of GW observations to base our analyses on, and discuss the key insights they provide in constraining predictions of momdified gravity theories.

%%%%%%%%%%%%%%%%%
\subsection{Parameter Inference}

@@

%We will consider the events GW150915~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.
%
%They are suitable for ringdown studies due to the high-masses and high signal-to-noise ratios (SNR).

%Although the LIGO-Virgo detectors have observed 90 GW signals, we select, for our analyses in this paper, the ones that are likely to be the most promising probes of the BH ringdown using our method. In~\cite{LIGOScientific:2021sio}, the \textit{pSEOBNRv4HM} analysis in Sec.VIII A.2 (which is most similar to the \pSEOB{} model presented in this paper) identified two events which provided the strongest bounds on the dominant QNM measuments -- GW150914~\cite{LIGOScientific:2016aoc} and GW200129~\cite{LIGOScientific:2021djp}.

\ag{event selection, noise, PE settings}
